taxize - taxonomic search and retrieval in R

### 2013-05-01 inst/doc/taxize_withcode_appA.tex
fixed gbif functions, updated slightly the appendix code

\begin{figure}[!ht] 
\centering 
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlfunctioncall{library}(doMC)
\hlfunctioncall{registerDoMC}(cores = 4)  \hlcomment{# I have a mac, so using doMC package, use whatever you like}
phylogeny <- \hlfunctioncall{phylomatic_tree}(taxa = \hlfunctioncall{as.character}(allnames$spname), taxnames = TRUE, 
    get = \hlstring{"POST"}, informat = \hlstring{"newick"}, method = \hlstring{"phylomatic"}, storedtree = \hlstring{"R20120829"}, 
    taxaformat = \hlstring{"slashpath"}, outformat = \hlstring{"newick"}, clean = \hlstring{"true"}, parallel = TRUE)
phylogeny$tip.label <- \hlfunctioncall{capwords}(phylogeny$tip.label, onlyfirst = TRUE)
\hlfunctioncall{plot}(phylogeny)
\end{alltt}
\end{kframe}

{\centering \includegraphics[width=.8\linewidth,height=4in]{figure/phylogeny}

@@

\begin{figure}[!ht] 
\centering 
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlfunctioncall{library}(doMC)
\hlfunctioncall{library}(rgbif)

@@

\hlcomment{# Make a map}
p <- rgbif::\hlfunctioncall{map}(occurr_list)
p
\end{alltt}
\end{kframe}

{\centering \includegraphics[width=\maxwidth,height=4in]{figure/map}

>>>>

\begin{figure}[!ht] 
\centering 
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
phylogeny <- \hlfunctioncall{phylomatic_tree}(taxa = \hlfunctioncall{as.character}(allnames$spname), taxnames = TRUE, 
    get = \hlstring{"POST"}, informat = \hlstring{"newick"}, method = \hlstring{"phylomatic"}, storedtree = \hlstring{"R20120829"}, 
    taxaformat = \hlstring{"slashpath"}, outformat = \hlstring{"newick"}, clean = \hlstring{"true"}, parallel = TRUE)
\end{alltt}
\begin{verbatim}

Retrieving data for species ' Helianthus annuus '

Retrieving data for species ' Pinus contorta '

Retrieving data for species ' Collomia grandiflora '

Retrieving data for species ' Abies magnifica '

Retrieving data for species ' Rosa californica '

Retrieving data for species ' Datura wrightii '

Retrieving data for species ' Mimulus bicolor '

Retrieving data for species ' Nicotiana glauca '

Retrieving data for species ' Madia sativa '

Retrieving data for species ' Bartlettia scaposa '
\end{verbatim}
\begin{alltt}
phylogeny$tip.label <- \hlfunctioncall{capwords}(phylogeny$tip.label, onlyfirst = TRUE)
\hlfunctioncall{plot}(phylogeny)
\end{alltt}
\end{kframe}

{\centering \includegraphics[width=\maxwidth]{figure/phylogeny}

@@

\begin{figure}[!ht] 
\centering 
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlfunctioncall{library}(rgbif)
\hlfunctioncall{library}(ggplot2)

@@

\hlcomment{# Make a map}
p <- \hlfunctioncall{gbifmap}(occurr_list) + \hlfunctioncall{guides}(col = \hlfunctioncall{guide_legend}(title = \hlstring{""}, nrow = 2, 
    byrow = TRUE)) + \hlfunctioncall{theme}(legend.position = \hlstring{"bottom"}, legend.key = \hlfunctioncall{element_blank}())
p
\end{alltt}
\end{kframe}

{\centering \includegraphics[width=\maxwidth]{figure/map}
